### 2023-03-06 Manuscript/Draft1.Rmd
manuscript update

The performance of estimates tend to decrease under increasing temperature, with the most dramatic changes seen in our VAST estimates without covariates. One exception to this is when we use a stratified mean approach while the population is decreasing. Since our analyses have found that the stratified mean tends to under estimate the true abundance, as the Yellowtail population decreases towards zero the difference between the estimate and the true value also decrease. That is, if the population is low enough, failing to appropriately sample the population produces the same result as appropriately sampling.

@@

As seen in Figure \@ref(fig:PopPct), in the constant temperature scenario the Cod population is decreasing its presence in strata 19 and 20 over the duration of the simulation in both seasons, while simultaneously increasing their presence in strata 16. However, an increase in average temperature had a seasonal impact on Cod's presence in strata 16 in our simulations. In the spring the population followed a similar trend of leaving 19 and 20 while simultaneously entering 16. However, in the fall the increasing temperature drives the population out of strata 16 and 21, and into 18, 22, and 24. **check the impact of this difference on estimates**

@@

>>>>

The performance of our abundance estimates tend to decrease under increasing temperature, with the most dramatic changes seen in our VAST estimates without covariates. One exception to this is when we use a stratified mean approach while the population is decreasing. Since our analyses have found that the stratified mean tends to under estimate the true abundance, as the Yellowtail population decreases towards zero the difference between the estimate and the true value also decrease. That is, if the population is low enough, failing to appropriately sample the population in a design-based method produces the same result as appropriately sampling.

@@

As seen in Figure \@ref(fig:PopPct), in the constant temperature scenario the Cod population is decreasing its presence in strata 19 and 20 over the duration of the simulation in both seasons, while simultaneously increasing presence in stratum 16. However, an increase in average temperature had a seasonal impact on Cod's presence in strata 16 in our simulations. In the spring the population followed a similar trend of leaving 19 and 20 while simultaneously entering 16, but in the fall the increasing temperature drives the population out of strata 16 and 21, and into 18, 22, and 24. **check the impact of this difference on estimates**

@@

Figure \@ref(fig:PopPct) reveals some subtle seasonal differences in the percent of haddock in each strata. In the constant temperature scenarios, the spring shows a decrease in strata 19 and 20 that correspond to increases in 16, 29 and 24. While strata 24 and 29 also increase in the fall under constant temperature, the corresponding decrease is primarily from strata 16 and 13. While similar results can be seen in the spring for the increasing temperature scenario, much more dramatic results exist in the fall under increasing temperature as we see a significant decreases in strata 13, 16, 21, and 22 that leads to the most noticable increases in strata 17, 18, and 29. This shift represents movement from the less deep and more centrally located strata towards exterior deeper strata.

### 2023-03-06 Manuscript/Draft1.tex
manuscript update

As seen in Figure \ref{fig:PopPct}, in the constant temperature scenario the Cod population is decreasing its presence in strata 19 and 20 over the duration of the simulation in both seasons, while simultaneously increasing their presence in strata 16. However, an increase in average temperature had a seasonal impact on Cod's presence in strata 16 in our simulations. In the spring the population followed a similar trend of leaving 19 and 20 while simultaneously entering 16. However, in the fall the increasing temperature drives the population out of strata 16 and 21, and into 18, 22, and 24. \textbf{check the impact of this difference on estimates}

@@

>>>>

As seen in Figure \ref{fig:PopPct}, in the constant temperature scenario the Cod population is decreasing its presence in strata 19 and 20 over the duration of the simulation in both seasons, while simultaneously increasing presence in stratum 16. However, an increase in average temperature had a seasonal impact on Cod's presence in strata 16 in our simulations. In the spring the population followed a similar trend of leaving 19 and 20 while simultaneously entering 16, but in the fall the increasing temperature drives the population out of strata 16 and 21, and into 18, 22, and 24. \textbf{check the impact of this difference on estimates}

@@

Figure \ref{fig:PopPct} reveals some subtle seasonal differences in the percent of haddock in each strata. In the constant temperature scenarios, the spring shows a decrease in strata 19 and 20 that correspond to increases in 16, 29 and 24. While strata 24 and 29 also increase in the fall under constant temperature, the corresponding decrease is primarily from strata 16 and 13. While similar results can be seen in the spring for the increasing temperature scenario, much more dramatic results exist in the fall under increasing temperature as we see a significant decreases in strata 13, 16, 21, and 22 that leads to the most noticable increases in strata 17, 18, and 29. This shift represents movement from the less deep and more centrally located strata towards exterior deeper strata.
